%-------------------------
% Resume in Latex
% Author : William Spongberg
% Credit: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large William Spongberg} & Email: \href{mailto:william@spongberg.dev}{william@spongberg.dev}\\
  \href{https://william.spongberg.dev}{william.spongberg.dev} & Mobile: +61 475 414 852 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Melbourne}{Melbourne, Australia}
{Bachelor of Computing and Software Systems}{Feb. 2022 -- June. 2025}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
{TransitEye}{React, TypeScript, Postgres}{Personal Project}
{}
\resumeItemListStart
\resumeItem{}{Engineered an open-source, full-stack web application to report and track public transport incidents in Melbourne.}
\resumeItem{}{Implemented an interactive map and custom heatmap using React and Leaflet to ensure easy visualisation and accessibility.}
\resumeItem{}{Utilised Supabase for user authentication and data storage, ensuring secure and fast access to the application.}
\resumeItemListEnd

\resumeSubheading
{Applify}{JavaScript, Generative AI}{Personal Project}
{}
\resumeItemListStart
\resumeItem{}{Built a Chrome web extension to analyse job board information and give realtime feedback to active users.}
\resumeItem{}{Utilised Google's local Gemini Nano API to generate tailored resume suggestions and improvements.}
\resumeItemListEnd

\resumeSubheading{Momentum Master App}
{TypeScript, Auth0, AWS, CICD, Flutter}{Team Member \& Full-Stack Developer}{}
\resumeItemListStart
\resumeItem{}{Developed a full-stack career progression application as part of a team of 5 for the client NoMoss.}
\resumeItem{}{Collaborated to complete 15+ epics over 12 weeks to align with the Agile methodology and client requirements.}
\resumeItem{}{Implemented and managed CICD pipelines via Vercel and GitLab for efficient deployment and testing.}
\resumeItem{}{Created fully featured REST API with 20+ endpoints for effective and secure data storage in AWS.}
\resumeItem{}{Created 80+ unit tests for the backend to ensure code quality and API security is maintained.}
\resumeItem{}{Conducted code reviews and provided constructive feedback to team members over scrums to enhance code quality.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

% Data Annotation
\resumeSubheading
{Data Annotation}{Remote}
{AI Reinforcement}{Apr 2024 - Present}
\resumeItemListStart
\resumeItem{}{Evaluated and annotated 1000+ lines of code across a variety of languages for AI models, ensuring high-quality training datasets.}
\resumeItem{}{Wrote detailed reports on code quality and custom solutions, providing valuable feedback to developers and AI models alike.}
\resumeItemListEnd

% Coles
\resumeSubheading
{Coles Group}{Melbourne, Australia}
{Retail Associate}{Dec 2020 - Present}
\resumeItemListStart
\resumeItem{}{Collaborated with team of 5-10 daily to unload and stock 3000+ items daily, improving store efficiency and customer satisfaction.}
\resumeItem{}{Gained experience in customer service and retail operations, enhancing communication skills.}
\resumeItem{}{Assisted in training new staff, fostering a collaborative work environment and improving team performance.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------VOLUNTEERING-----------------
\section{Volunteering}
\resumeSubHeadingListStart

\resumeSubheading
{Fitzroy High School}{Melbourne, Australia}
{Volunteer Teacher's Assistant}{Apr 2024 - May 2024}
\resumeItemListStart
\resumeItem{}{Assisted teachers in classroom management and provided both educational support and mentorship to students.}
\resumeItem{}{Organised educational activities and resources to enhance student engagement and my own understanding of effective communication, leadership and alternative learning.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\item{\textbf{Languages:} Java, JavaScript, TypeScript, Python, C, C\#, SQL, Dart, Prolog, Haskell}
\item{\textbf{Technologies:} Git, VSCode, IntelliJ, MySQL, Android Studio, Flutter, Node.js, Supabase, AWS}
\item{\textbf{Project Management \& Collaboration:} Slack, Jira, Confluence, Trello, Agile Methodology}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
